Forecasting the United States 2024 Presidential Election

### 2024-11-04 paper/paper.qmd
added cites

Prediction betting markets provide a new data source that may be valuable for predicting the outcome of the US election. These online betting markets allow people to buy shares that represent an outcome of some event. If the event occurs then the share is worth $1, if not then the share's price falls to 0. This means the live share price reflects the probability of the event occurring. For example, for the outcome of the presidential election market, if Trump's share price is 65 cents this means the market is predicting there is a 65% chance that Trump will win the election. Recently the trading volume on these markets is significant, which indicates that these markets may be helpful in predicting election outcomes. Some papers have included data from these markets in their models to improve their prediction accuracy.[REF https://anderson-review.ucla.edu/wp-content/uploads/2024/10/voter_preferences_updated.pdf].

@@

On the other hand the main disadvantage is that all of the investors in this market essentially completely anonymous. This means there is no way of checking whether a large investor, who has significant price setting power, is indeed sophisticated or not. Furthermore, because these markets have only recently become popular or even legal in some cases one might expect these markets to be full of amateurs. These markets may display a bais as well, where the largest market Polymarket [REF] is based on crypto-currency, and Trump is popular among crypto-enthusiasts, and large financial institutions are underrepresented in the crypto-market.

@@

=======
>>>>>>> 3831a5556d47b44b38240855a1f7d590aa816a2d
\newpage

>>>>

Prediction betting markets provide a new data source that may be valuable for predicting the outcome of the US election. These online betting markets allow people to buy shares that represent an outcome of some event. If the event occurs then the share is worth $1, if not then the share's price falls to 0. This means the live share price reflects the probability of the event occurring. For example, for the outcome of the presidential election market, if Trump's share price is 65 cents this means the market is predicting there is a 65% chance that Trump will win the election. Recently the trading volume on these markets is significant, which indicates that these markets may be helpful in predicting election outcomes. Some papers have included data from these markets in their models to improve their prediction accuracy (@market_paper).

@@

On the other hand the main disadvantage is that all of the investors in this market essentially completely anonymous. This means there is no way of checking whether a large investor, who has significant price setting power, is indeed sophisticated or not. Furthermore, because these markets have only recently become popular or even legal in some cases one might expect these markets to be full of amateurs. These markets may display a bais as well, where the largest market Polymarket is based on crypto-currency, and Trump is popular among crypto-enthusiasts, and large financial institutions are underrepresented in the crypto-market.

@@
